---
title: "Labwork №1. Creating base of typical Data Science project"
author: "&copy; [Andrew Zaykin](https://www.linkedin.com/in/zaykinandrew/), `r format(Sys.time(), '%Y')`"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: yes
    toc_float: true
    highlight: tango
    code-fold: true
    code-line-numbers: true
    code-tools: true
    code-copy: true
fontsize: 12pt
lang: ukr
header-includes:
 \usepackage[T2A]{fontenc}
 \usepackage[utf8]{inputenc}
 \usepackage[russian]{babel}
editor_options: 
  chunk_output_type: console
bibliography: source/references_lab.bib
---

## Introduction

In this labwork we will learn:

* how to import data and visualize it in RMarkdown using ggplot2 library
* how to create interactive documents using RMarkdown
* how to use Latex for formulas in RMarkdown
* how to create bibliography using BibTeX

## Task completion

1. Import point coordinates using rio library [@rio]

```{r}
library(rio)
coordinates_data <- import("source/data/data.csv")
```

2. Create graph of function by coordinates using ggplot2 library [@ggplot2]

```{r}
library(ggplot2)

ggplot(data = coordinates_data, aes(x = x, y = y)) +
  geom_line(color = "blue", linewidth = 1) +
  geom_point(color = "red", size = 2) +
  theme_dark() +
  theme(plot.title = element_text(size = 10)) +
  labs(title = "Graph of function by coordinates",
       x = "X",
       y = "Y")
```

3. But this code is not optimal. We can use stream operator `%>%` to make it more readable.

```{r}
library(magrittr)

coordinates_data %>%
  ggplot(aes(x = x, y = y)) +
  geom_line(color = "green", linewidth = 1) +
  geom_point(color = "red", size = 2) +
  theme_dark() +
  theme(plot.title = element_text(size = 10)) +
  labs(title = "Graph of function by coordinates using %>% operator",
       x = "X",
       y = "Y")
```

4. The formula of this function is $y = 2 + 3 * x + 1.57 * x^2$.

## References
